---
title: ""
format:
  pdf:
    output-file: KHL_CV.pdf
    template: assets/cv-template.tex
    keep-tex: true
    pdf-engine: xelatex
---

```{r setup, include=FALSE}
library(yaml)
# Ensure user libraries are visible (bib2df may be installed under another R minor)
source("scripts/_libpaths.R")
suppressPackageStartupMessages(library(bib2df))

edu      <- yaml::read_yaml("data/education.yml")
appts    <- yaml::read_yaml("data/appointments.yml")
grants   <- yaml::read_yaml("data/grants.yml")
awards   <- yaml::read_yaml("data/awards.yml")
talks    <- yaml::read_yaml("data/talks.yml")
teaching <- yaml::read_yaml("data/teaching.yml")[[1]]
service  <- yaml::read_yaml("data/service.yml")
# Translated editions, keyed by BibTeX citation key — kept out of the .bib so
# the CJK titles never pass through bib2df (and never reach the website JSON,
# which selects a fixed column set that would drop them anyway).
translations <- yaml::read_yaml("data/translations.yml")

# ── Load publications from BibTeX ────────────────────────────────────────────
bib_raw <- bib2df::bib2df("publications/publications.bib")
names(bib_raw) <- tolower(names(bib_raw))
for (col in c("doi","journal","publisher","booktitle","volume","number",
              "pages","howpublished","note")) {
  if (!col %in% names(bib_raw)) bib_raw[[col]] <- NA_character_
}
bib_type_map <- c(article = "article", book = "book",
                  incollection = "chapter", inproceedings = "chapter",
                  unpublished = "working", techreport = "working",
                  misc = "other")
pubs <- data.frame(
  key     = bib_raw$bibtexkey,
  type    = unname(ifelse(is.na(bib_type_map[tolower(bib_raw$category)]),
                          "other", bib_type_map[tolower(bib_raw$category)])),
  year    = as.integer(bib_raw$year),
  title   = bib_raw$title,
  authors = vapply(bib_raw$author,
                   function(a) paste(a, collapse = " and "),
                   character(1)),
  journal   = bib_raw$journal,
  publisher = bib_raw$publisher,
  booktitle = bib_raw$booktitle,
  volume    = bib_raw$volume,
  number    = bib_raw$number,
  pages     = bib_raw$pages,
  howpub    = bib_raw$howpublished,
  note      = bib_raw$note,
  doi       = bib_raw$doi,
  stringsAsFactors = FALSE
)

cat_md <- function(...) cat(paste0(..., collapse = "\n"))

yr <- function(x) if (!is.null(x$years)) x$years else as.character(x$year)

# Escape LaTeX-special characters in text fields
ltx <- function(s) {
  if (is.null(s) || is.na(s)) return("")
  s <- as.character(s)
  s <- gsub("\\\\", "\\\\textbackslash{}", s)
  s <- gsub("([&%$#_{}])", "\\\\\\1", s)
  s <- gsub("~", "\\\\textasciitilde{}", s)
  s <- gsub("\\^", "\\\\textasciicircum{}", s)
  s
}

# Two-column longtable, emitted as a raw LaTeX block so Pandoc doesn't rewrite it
two_col <- function(rows) {
  paste0(
    "\n```{=latex}\n",
    "\\begin{longtable}{@{}p{1in}p{5.3in}@{}}\n",
    paste(rows, collapse = " \\\\\n"),
    " \\\\\n\\end{longtable}\n",
    "```\n"
  )
}
```



# Appointments

```{r, echo=FALSE, results='asis'}
rows <- sapply(appts, function(x)
  sprintf("%s & %s, %s", ltx(yr(x)), ltx(x$title), ltx(x$institution)))
cat_md(two_col(rows))
```
# Education

```{r, echo=FALSE, results='asis'}
rows <- sapply(edu, function(x)
  sprintf("%s & %s, %s", ltx(x$year), ltx(x$degree), ltx(x$institution)))
cat_md(two_col(rows))
```

# Publications

```{r, echo=FALSE, results='asis'}
types <- list(
  list(label = "Books",                filter = "book"),
  list(label = "Refereed Articles",    filter = "article"),
  list(label = "Book Chapters",        filter = "chapter"),
  list(label = "Working Papers",       filter = "working"),
  list(label = "Op-Eds, Book Reviews, and Other", filter = "other")
)

# BibTeX gives "Last, First" — keep first author as-is, invert subsequent ones.
uninvert <- function(name) {
  name <- trimws(name)
  if (!grepl(",", name)) return(name)
  m <- regmatches(name, regexec("^([^,]+),\\s*(.+)$", name))[[1]]
  if (length(m) == 3) paste(m[3], m[2]) else name
}

fmt_authors_asa <- function(s) {
  parts <- trimws(strsplit(s, "\\s+and\\s+")[[1]])
  if (length(parts) == 0) return("")
  if (length(parts) > 1) parts[-1] <- vapply(parts[-1], uninvert, character(1))
  bold <- function(x) ifelse(grepl("Ken-?Hou", x) & grepl("Lin", x),
                             paste0("\\textbf{", x, "}"), x)
  parts <- bold(parts)
  if (length(parts) == 1) return(parts)
  if (length(parts) == 2) return(paste(parts[1], "and", parts[2]))
  paste0(paste(parts[-length(parts)], collapse = ", "),
         ", and ", parts[length(parts)])
}

# Build "vol(num):pages" from bib components
vip_string <- function(p) {
  has_v <- !is.na(p$volume) && nchar(p$volume)
  has_n <- !is.na(p$number) && nchar(p$number)
  has_p <- !is.na(p$pages)  && nchar(p$pages)
  pp <- if (has_p) gsub("--", "-", p$pages) else ""
  if (has_v && has_n && has_p) return(sprintf("%s(%s):%s", p$volume, p$number, pp))
  if (has_v && has_p)          return(sprintf("%s:%s", p$volume, pp))
  if (has_p)                   return(pp)
  if (has_v && has_n)          return(sprintf("%s(%s)", p$volume, p$number))
  if (has_v)                   return(p$volume)
  ""
}

# Translated editions hang off the book entry as sub-items.
fmt_translations <- function(key) {
  eds <- translations[[key]]
  if (is.null(eds) || !length(eds)) return("")
  items <- vapply(eds, function(e) sprintf(
    "\\item %s edition (%s). %s: %s.",
    ltx(e$language), ltx(as.character(e$year)),
    ltx(e$city), ltx(e$publisher)),
    character(1))
  paste0(
    "\n```{=latex}\n",
    "\\vspace{-0.6\\baselineskip}\n",
    "\\begin{itemize}[left=1.5em, nosep]\n",
    paste(items, collapse = "\n"),
    "\n\\end{itemize}\n```\n\n"
  )
}

fmt_pub <- function(p) {
  doi_link <- if (!is.na(p$doi) && nchar(p$doi))
    sprintf(' \\href{https://doi.org/%s}{[DOI]}', p$doi) else ""
  authors <- fmt_authors_asa(p$authors)
  year <- ltx(as.character(p$year))
  title <- ltx(p$title)
  vip <- ltx(vip_string(p))

  body <- switch(as.character(p$type),
    book = {
      pub <- if (!is.na(p$publisher)) ltx(p$publisher) else ""
      sprintf("\\emph{%s}.%s", title,
              if (nchar(pub)) paste0(" ", pub, ".") else "")
    },
    article = {
      jrn <- if (!is.na(p$journal)) ltx(p$journal) else ""
      pages <- if (nchar(vip)) paste0(" ", vip, ".") else ""
      sprintf("\"%s.\" \\emph{%s}%s", title, jrn, pages)
    },
    chapter = {
      bt <- if (!is.na(p$booktitle)) ltx(p$booktitle) else ""
      pp <- if (nchar(vip)) sprintf("Pp. %s in ", vip) else ""
      sprintf("\"%s.\" %s\\emph{%s}.", title, pp, bt)
    },
    working = {
      venue <- if (!is.na(p$howpub) && nchar(p$howpub)) ltx(p$howpub)
               else if (!is.na(p$note) && nchar(p$note)) ltx(p$note) else ""
      sprintf("\"%s.\" Working Paper%s", title,
              if (nchar(venue)) paste0(", ", venue, ".") else ".")
    },
    other = {
      venue <- if (!is.na(p$journal)) ltx(p$journal)
               else if (!is.na(p$howpub)) ltx(p$howpub) else ""
      sprintf("\"%s.\"%s", title,
              if (nchar(venue)) paste0(" \\emph{", venue, "}.") else "")
    }
  )

  sprintf("%s. %s. %s%s\n\n%s", authors, year, body, doi_link,
          fmt_translations(p$key))
}

for (t in types) {
  sub <- pubs[pubs$type == t$filter, ]
  if (nrow(sub) == 0) next
  sub <- sub[order(-sub$year), ]
  cat_md(sprintf("\n## %s\n\n", t$label))
  cat_md(sapply(seq_len(nrow(sub)), function(i) fmt_pub(sub[i,])))
}
```

# Honors & Awards

```{r, echo=FALSE, results='asis'}
rows <- sapply(awards, function(x)
  sprintf("%s & %s, %s", ltx(yr(x)), ltx(x$name), ltx(x$org)))
cat_md(two_col(rows))
```

# Grants & Fellowships

```{r, echo=FALSE, results='asis'}
rows <- sapply(grants, function(x) {
  amt <- if (!is.null(x$amount)) paste0(" $\\cdot$ ", ltx(x$amount)) else ""
  sprintf("%s & \\textbf{%s}\\newline %s $\\cdot$ %s%s",
          ltx(yr(x)), ltx(x$title), ltx(x$role), ltx(x$funder), amt)
})
cat_md(two_col(rows))
```



# Presentations

```{r, echo=FALSE, results='asis'}
years <- sort(unique(sapply(talks, `[[`, "year")), decreasing = TRUE)
for (y in years) {
  yr_talks <- Filter(function(x) x$year == y, talks)
  cat_md(sprintf("\n**%s**\n\n", y))
  items <- sapply(yr_talks, function(x) {
    inv <- if (isTRUE(x$invited)) " *(Invited)*" else ""
    sprintf('- \"%s.\" %s, %s.%s\n',
            ltx(x$title), ltx(x$venue), ltx(x$location), inv)
  })
  cat_md(items)
}
```

# Teaching

```{r, echo=FALSE, results='asis'}
cat_md(sprintf("**%s**\n\n", ltx(teaching$institution)))
cat_md("*Graduate*\n\n")
cat_md(paste0("- ", sapply(teaching$graduate, ltx), "\n"))
cat_md("\n*Undergraduate*\n\n")
cat_md(paste0("- ", sapply(teaching$undergraduate, ltx), "\n"))
```

## Graduate Advising

```{r, echo=FALSE, results='asis'}
cat_md("*Dissertation Committee Chair*\n\n")
rows <- sapply(service$advising$dissertation_chair, function(x)
  sprintf("%s & %s (%s)", ltx(x$years), ltx(x$name), ltx(x$role)))
cat_md(two_col(rows))

cat_md("\n*Dissertation Committee Member*\n\n")
rows <- sapply(service$advising$dissertation_committee, function(x)
  sprintf("%s & %s", ltx(x$years), ltx(x$name)))
cat_md(two_col(rows))

```

# Service

## Editorial Positions

```{r, echo=FALSE, results='asis'}
rows <- sapply(service$editorial, function(x)
  sprintf("%s & %s, \\emph{%s}", ltx(x$years), ltx(x$role), ltx(x$org)))
cat_md(two_col(rows))
```

## Peer Review

```{r, echo=FALSE, results='asis'}
# Flat name lists — run-in paragraphs rather than two_col, which expects
# a "years & entry" pair per row.
rev_list <- function(x) paste(sapply(x, ltx), collapse = ", ")

cat_md("*Journals*\n\n", rev_list(service$reviewer$journals), "\n")
cat_md("\n*Grant Agencies*\n\n", rev_list(service$reviewer$grant_agencies), "\n")
cat_md("\n*Tenure and Promotion*\n\n", rev_list(service$reviewer$tenure_promotion), "\n")
```

## Professional Associations

```{r, echo=FALSE, results='asis'}
rows <- sapply(service$professional_associations, function(x)
  sprintf("%s & %s, %s", ltx(x$years), ltx(x$role), ltx(x$org)))
cat_md(two_col(rows))
```

## University Service

```{r, echo=FALSE, results='asis'}
cat_md("*Departmental*\n\n")
rows <- sapply(service$university$departmental, function(x)
  sprintf("%s & %s", ltx(x$years), ltx(x$role)))
cat_md(two_col(rows))

cat_md("\n*College-wide*\n\n")
rows <- sapply(service$university$college_wide, function(x)
  sprintf("%s & %s", ltx(x$years), ltx(x$role)))
cat_md(two_col(rows))

cat_md("\n*University-wide*\n\n")
rows <- sapply(service$university$university_wide, function(x)
  sprintf("%s & %s", ltx(x$years), ltx(x$role)))
cat_md(two_col(rows))
```


